### 2012-02-13 paper.tex
Proof-reading

\documentclass[8.5pt,twoside,twocolumn]{article}
\oddsidemargin -1.2cm
\evensidemargin -1.2cm
\textwidth 18cm
\headheight 1.0in
\topmargin -3.5cm
\textheight 22cm
\usepackage[super,sort&compress,comma]{natbib} 
\usepackage{mhchem}
\usepackage[utf8]{inputenc}
\usepackage{times,mathptmx}
% \usepackage{times}
% feel free not to use mathptmx if it causes difficulties
\usepackage{sectsty}
\usepackage{balance}

@@

\noindent \normalsize{High-quality mass spectrometry data of the oscillatory behaviour of CO oxidation on silicon dioxide supported Pt-nanoparticles at atmospheric pressure is presented. The oscillations are self-sustained for several days at constant temperature, pressure and CO/O$_2$ ratio. The frequency of the oscillations is very well defined and show clear tendency to increase in with time. A plausible mechanism for the oscillations is proposed based on an earlier model on Pd single crystals [Hendriksen \textit{et al., Nature Chemistry}, 2010, \textbf{9}, 730]}
\vspace{0.5cm}
 \end{@twocolumnfalse}
  ]

@@

%BEMAERK! Denne tekst er nakket fra et tidligere paper (Carbon,2011). Pre-formed mass-selected platinum particles were soft-landed onto the reactor at room temperature using an inert gas-aggregation source (Mantis Deposition Ltd., Nanogen 50). The particles are formed by gas-phase condensation from a flux of platinum atoms that are sputtered from a 99.99\% pure Ru target using a magnetron sputter source. The magnetron is housed in a liquid nitrogen cooled enclosure with a 3\,mm diameter aperture at one end. Argon gas is flown into the volume around the magnetron at a rate of 10-120 sccm and is pumped away via the aperture so that a local pressure of 0.1-1 mbar  is obtained inside the gas-aggregation zone during operation. The cooled argon gas thermalises the sputtered platinum atoms so that they condense into clusters, which further coalesce to form nanoparticles. The size of the nanoparticles is determined by a number of factors such as magnetron sputter power (typically 20–40 W), rate of gas flow, distance between the target and the exit aperture and the diameter of the exit aperture. Platinum nanoparticles with diameters in the range of 2–16 nm can be produced using the source \cite{Nielsen2010,Nielsen2009}. The nanoparticles are carried by the gas stream through the exit aperture of the aggregation zone, producing a nanoparticle beam that is further refined by a skimmer. The nanoparticle beam is then passed through a quadrupole mass filter where the ionised fraction (60-80\%) of the nanoparticles can be filtered according to their mass-to-charge ratio.

@@

\begin{figure}[h]
\centering
  \includegraphics[width=9cm]{temperature_dependence.png}
  \caption{After about 10 hours of oscillations at 205$^\circ$C the temperature is first lowered by 5$^\circ$C and soon after increased by 2$^\circ$C. Before the temperature step the oscillation period was approximately 500\,s and after the step the period is approximately 5000\,s}
  \label{fgr:temperature_dependence}
\end{figure}
A very strong temperature dependence on the oscillation frequency was also found as shown in Figure~\ref{fgr:temperature_dependence}. By changing the temperature 5$^\circ$C the oscillation period is changed by more than a factor of 10. The magnitude of the change is not completely consistent across all measured samples, but all samples do show a very large temperature dependency, in some cases a change of a few degrees will consistently turn on and off the oscillations.

@@

According to the proposed model, the bare metal surface is less active than the oxidized surface. It is further suggested that a high concentration of steps will thermodynamically favor the reduced surface and a low concentration of steps will favor the oxidized surface. The oscillating behavior is hence attributed to the shift between an oxidized surface which will increase surface roughness and a reduced surface which will decrease surface roughness. Thus the reaction will only run a given time in the high-rate state before the catalyst will expose the reduced surface and thus lower the rate. After some time, the roughness will again be sufficiently low that the catalyst will again oxidize and increase the rate.

In this study, we measure on Pt nanoparticles which, compared to a single crystal or a thin film, is a very rough surface. It is to be expected that the particles will initially favor the reduced state. As the reaction runs, the conditions toward the outlet of the reactor will become more reducing and at the same time, the reaction itself will smoothen the particles, further pushing towards an oxidation of the particles. Gradually as the particles towards the outlet oxidizes the turn-over will increase and the general CO concentration will decrease, further promoting more and more particles to oxidize which will gradually be seen in the mass-spectrometry as an increase in CO$_2$ and a decrease in CO.

Even though the temperature is kept constant, the light-off temperature will decrease as the CO-concentration increases, and at a given point the CO concentration will become low enough that the light-off temperature drops below the sample temperature and the sample will show full conversion. If not all particles are oxidized at this point they will oxidize much faster after light-off due to the low CO-concentration. The further increased rate will not be visible in the mass-spectrometer since the reactor is already in full conversion. As most of the particles are now oxidized they will become more and more roughened and gradually return to the reduced state. Fewer and fewer oxidized particles will be responsible for the activity increasing the roughness rate of the remaining active particles. Just before the overall activity drops only a very small fraction of the particles actually participates in the reaction and the de-activation will happen very suddenly once these few particles eventually becomes sufficiently rough that they will reduce and lose activity.

@@

An interesting feature in the data, is the very large temperature dependence. This property was actually predicted by Hendriksen et. al \cite{Hendriksen2010} when they proposed the model, and to our knowledge, this is the first time the temperature dependence is measured.

\section{Conclusion}
We have for the first time demonstrated oscillating CO oxidation on Pt nanoparticles measured with high-quality mass-spectrometry. We have found that the samples will increasing the oscillation period over time and show a dramatic temperature dependence. Oscillations has been seen on a wide range of nanoparticles from 3\,nm to 9\,nm and within a large CO-concentration window, however, it is evident that very oxygen rich conditions is needed for the oscillations to happen.

>>>>

\documentclass[8.5pt,twoside,twocolumn]{article}
\oddsidemargin -1.2cm
\evensidemargin -1.2cm
\textwidth 18cm
\headheight 1.0in
\topmargin -3.5cm
\textheight 22cm
\usepackage[super,sort&compress,comma]{natbib} 
\usepackage[version=3]{mhchem}
\usepackage[utf8]{inputenc}
\usepackage{times,mathptmx}
% \usepackage{times}
% feel free not to use mathptmx if it causes difficulties
\usepackage{sectsty}
\usepackage{balance}

@@

\noindent \normalsize{High-quality mass spectrometry data of the oscillatory behavior of CO oxidation on silicon dioxide supported Pt-nanoparticles at atmospheric pressure has been performed. The oscillations are self-sustained for several days at constant temperature, pressure and CO/O$_2$ ratio. The frequency of the oscillations is very well defined and increases with time. The oscillation frequency is furthermore strongly temperature temperature dependent with increasing temperature resulting in increasing frequency. A plausible mechanism for the oscillations is proposed based on a oxidation/reduction cycle of the nanoparticles which change the change rate of CO oxidation on the particles.}  %on an earlier model on Pd single crystals [Hendriksen \textit{et al., Nature Chemistry}, 2010, \textbf{9}, 730]}
\vspace{0.5cm}
 \end{@twocolumnfalse}
  ]

@@

@@

\begin{figure}[h]
\centering
  \includegraphics[width=9cm]{temperature_dependence.png}
  \caption{After about 10 hours of oscillations at 205$^\circ$C the temperature is first lowered by 5$^\circ$C and soon after increased by 2$^\circ$C. Before the temperature step the oscillation period was approximately 500\,s and after the step the period is approximately 5000\,s.}
  \label{fgr:temperature_dependence}
\end{figure}
A very strong temperature dependence on the oscillation frequency was also found as shown in Figure~\ref{fgr:temperature_dependence}. By changing the temperature 5$^\circ$C the oscillation period is changed by more than a factor of 10. The magnitude of the change is not completely consistent across all measured samples but all samples do show a very large temperature dependency where in some cases a provoked small change in temperature will consistently turn on and off the oscillations.

@@

According to the proposed model the bare metal surface is less active than the oxidized surface. It is further suggested that a high concentration of steps will thermodynamically favor the reduced surface and a low concentration of steps will favor the oxidized surface. The oscillating behavior is hence attributed to the shift between an oxidized surface which will increase surface roughness and a reduced surface which will decrease surface roughness. Thus, the reaction will only run a given time in the high-rate state before the catalyst will expose the reduced surface and lower the rate. After some time, the roughness will again be sufficiently low that the catalyst will again oxidize and increase the rate.

In this study Pt nanoparticles were investigated which, compared to a single crystal or a thin film, is a very rough surface. It is to be expected that the particles will initially favor the reduced state. As the reaction runs, the conditions toward the outlet of the reactor will become more reducing and at the same time the reaction itself will smoothen the particles further pushing towards an oxidation of the particles. Gradually as the particles toward the outlet oxidizes the turn-over will increase and the general CO concentration will decrease promoting more and more particles to oxidize which will gradually be seen in the mass-spectrometry as an increase in CO$_2$ and a decrease in CO.

Even though the temperature is kept constant the light-off temperature will decrease as the CO-concentration increases. At a given point the CO concentration will become low enough that the light-off temperature drops below the sample temperature and the sample will show full conversion. If not all particles are oxidized at this point they will oxidize much faster after light-off due to the low CO-concentration. The further increased rate will not be visible in the mass-spectrometer since the reactor is already in full conversion. As most of the particles are now oxidized they will become more and more roughened and gradually return to the reduced state. Fewer and fewer oxidized particles will be responsible for the activity increasing the roughness rate of the remaining active particles. Just before the overall activity drops only a very small fraction of the particles actually participates in the reaction and the de-activation will happen very suddenly once these few particles eventually becomes sufficiently rough that they will reduce and lose activity.

@@

An interesting feature in the data is the very large temperature dependence. This property agrees well an earlier suggested model \cite{Hendriksen2010} and is, to our knowledge, the first time the temperature dependence of oscillations at atmospheric pressure is measured.

\section{Conclusion}
Self-sustained CO oxidation oscillations at atmospheric pressure on Pt nanoparticles ranging from from 3\,nm to 9\,nm have been measured with high-quality mass-spectrometry. It was found that the samples increased the oscillation period over time and showed a strong temperature dependence. A model is proposed where the nanoparticles go through repetitive oxidation/reduction cycles which change the change rate of CO oxidation on the particles.
